Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-06-30 paper/AlignedIsotropicGW.tex
Extended Data stuff in TIFF or EPS (ugh).

\begin{table}
\begin{centering}
\begin{tabular}{ c |  c  |  c  | c  }
  \hline 
  \hline
Events & $\sigma_{I/A}$ &  $\sigma_{I/A}$ & $\sigma_{I/A}$ \\ 
 & ``Low'' & ``Flat'' & ``High'' \\ \hline
GW150914 and GW151226 &  1.3 & 2.2 & 3.7 \\ %\hline
All O1 events & 1.7 & 2.7 & 4.4 \\ %\hline
All O1 events and GW170104 & \textbf{2.4} & 3.5 & 5.4 \\ \hline
\end{tabular}
\caption[]{Significance $\sigma_{I/A}$ of the odds ratio between the isotropic and aligned models using just GW150914 and GW151226, all 3 O1 events, and all 4 currently observed events (including GW170104). The number in bold is the result we quote in the main text.}
\label{tab:accumulation}
\end{centering}
\end{table}

>>>>

\begin{table}
\begin{centering}
% \begin{tabular}{ c |  c  |  c  | c  }
%   \hline 
%   \hline
% Events & $\sigma_{I/A}$ &  $\sigma_{I/A}$ & $\sigma_{I/A}$ \\ 
%  & ``Low'' & ``Flat'' & ``High'' \\ \hline
% GW150914 and GW151226 &  1.3 & 2.2 & 3.7 \\ %\hline
% All O1 events & 1.7 & 2.7 & 4.4 \\ %\hline
% All O1 events and GW170104 & \textbf{2.4} & 3.5 & 5.4 \\ \hline
% \end{tabular}
\caption[]{\textbf{Significance $\sigma_{I/A}$ of the odds ratio between the isotropic and aligned models.} The odds ratio is computed using just GW150914 and GW151226, all 3 O1 events, and all 4 currently observed events (including GW170104). The number in bold is the result we quote in the main text.}
\label{tab:accumulation}
\end{centering}
\end{table}
